Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-28 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:28	22:01:27	(Fri28.Aug)

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}

@@

>>>>

\newcommand\multimedia[1]{\textbf{{\color{red}[#1]}}}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{LCA images using window sets with varying parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}

@@

Media file \multimedia{Media Movie 1} shows how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$. It demonstrates that at $L$=1 the window responses are rectangular in all areas in the image. At $L$=2 we can observe that pixels in highlight are processed with windows with slightly varying amplitude responses, but with zero locations on similar locations and highlight regions being
